Outline--Draft JCP format for: Reactive Force Field for Solid Oxides Containing Lanthanum

### 2019-06-13 Paper/paper.tex
Update paper.tex
Added default scale for image
Updates from Overleaf

ReaxFF is a force field based on the dynamical computation of the bond-order, which dictates the connectivity between atoms on the fly.
This approach allows ReaxFF to consider bond breaking and formation, and therefore the ability to follow the apparition of intermediates involved in the reaction mechanism in complex systems containing thousands of atoms.\cite{migliorati_development_2017,merinov_reaxff_2014,
raymand_reactive_2008,
shin_development_2015,
van_duin_reaxff_2008,
goddard_development_2006,
hubin_parameterization_2016,
senftle_reaxff_2016,
chenoweth_reaxff_2009,
chenoweth_reaxff_2008,
van_duin_reaxff_2008-1,
liu_reaxff-lg:_2011}

Its use bridges the advantages of classical molecular dynamics simulation with those of quantum--mechanical approaches.

>>>>

ReaxFF is a force field based on the dynamical computation of the bond-order, which dictates the connectivity between atoms on the fly.
This approach allows ReaxFF to consider bond breaking and formation, and therefore permits to follow the apparition of intermediates.
In complex systems this ability proves to be invaluable for following reaction mechanism when the number of atoms are in the order of thousands or higher.\cite{migliorati_development_2017,merinov_reaxff_2014,
raymand_reactive_2008,
shin_development_2015,
van_duin_reaxff_2008,
goddard_development_2006,
hubin_parameterization_2016,
senftle_reaxff_2016,
chenoweth_reaxff_2009,
chenoweth_reaxff_2008,
van_duin_reaxff_2008-1,
liu_reaxff-lg:_2011}
This way, ReaxFF bridges classical molecular dynamics and quantum--mechanical approaches while avoiding exponential scaling of calculation times.
